02_DESeq_characterization

### 2019-11-22 analysis/03_DESeq2_characterization.Rmd
now with some IEGs

GOterms <- rbind(parentalbehavior, reproduction, behavior, systemdevelopment, endocrineprocess)

@@

returnGOgenes <- function(whichGOterms, data){

  df <- inner_join(whichGOterms, data) %>% filter(direction != "NS") %>%  select(gene, GO) %>% 
  group_by(GO) %>% summarize(genes = str_c(gene, collapse = ", "))
  return(df)
}

dt1 <- returnGOgenes(GOterms,control.bldg) 
kable(dt1)

dt2 <- returnGOgenes(GOterms,bldg.lay) 
kable(dt2)

dt3 <- returnGOgenes(GOterms,lay.inc.d3)  
kable(dt3)

dt4 <- returnGOgenes(GOterms,inc.d3.inc.d9)  
kable(dt4)

dt5 <- returnGOgenes(GOterms,inc.d9.inc.d17)  
kable(dt5)

dt6 <- returnGOgenes(GOterms,inc.d17.hatch)  
kable(dt6)

dt7 <- returnGOgenes(GOterms,hatch.n5)  
kable(dt7)

dt8 <- returnGOgenes(GOterms,n5.n9) 
kable(dt8)

>>>>

responsetostimulus <- read.table("../results/goterms/responsetostimulus.txt", sep = "\t", row.names = NULL,  fill=TRUE)
responsetostimulus$GO <- "response to external stimulus, GO:0009605"

GOterms <- rbind(parentalbehavior, reproduction, behavior, 
                 systemdevelopment, endocrineprocess, responsetostimulus)

@@

returnGOgenes <- function(whichGOterms, data, mycomparison){

  df <- inner_join(whichGOterms, data) %>% 
    filter(direction != "NS") %>%  
    select(gene, GO) %>% 
    group_by(GO) %>% 
    summarize(genes = str_c(gene, collapse = ", "))  %>% 
    mutate(comparison = mycomparison) %>% 
    select(comparison, GO, genes)

  return(df)
}

dt1 <- returnGOgenes(GOterms,control.bldg, "control v bldg") 
dt2 <- returnGOgenes(GOterms,bldg.lay , "bldg v lay") 
dt3 <- returnGOgenes(GOterms,lay.inc.d3 , "lay v inc d3")  
dt4 <- returnGOgenes(GOterms,inc.d3.inc.d9 , "inc d3 v inc d9")  
dt5 <- returnGOgenes(GOterms,inc.d9.inc.d17 , "inc d9 v inc d17")  
kable(dt5)

dt6 <- returnGOgenes(GOterms,inc.d17.hatch, "inc d17 v hatch")  
dt7 <- returnGOgenes(GOterms,hatch.n5, "hatch v n5")  
kable(dt7)

dt8 <- returnGOgenes(GOterms,n5.n9, "n5 v n9")

alldt <- rbind(dt1,dt2,dt3,dt4,dt5,dt6,dt7,dt8)
alldt

write.csv(alldt, "../results/03_GO_femalepituitary.csv")
```
